Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2015-01-27 Paper/ms.tex
Jones et al reference

\subsection{Trans-dimensional MCMC}
Trans-dimensional MCMC methods such as birth-death MCMC \citep{birthdeath} or the
more general reversible jump MCMC \citep{green} treat the model dimension
$N$ as just another model parameter. At fixed $N$, standard techniques such
as the Metropolis algorithm can be used to explore the posterior distribution.
Additional moves that propose to change the value of $N$ are also defined. The
simplest of these are birth-death moves. More complicated moves, such as
split-and-merge are possible but not always necessary.
Trans-dimensional MCMC is a natural tool for a wide range of astronomical
data analysis problems \citep[e.g.][]{umstatter, walmswell, starfield}.

@@

>>>>

\subsection{Trans-dimensional MCMC}
Trans-dimensional MCMC methods such as birth-death MCMC \citep{birthdeath} or the
more general reversible jump MCMC \citep{green} treat the model dimension
$N$ as just another model parameter. At fixed $N$, standard techniques such
as the Metropolis algorithm can be used to explore the posterior distribution.
Additional moves that propose to change the value of $N$ are also defined. The
simplest of these are birth-death moves. More complicated moves, such as
split-and-merge, are possible but not always necessary.
Trans-dimensional MCMC is a natural tool for a wide range of astronomical
data analysis problems \citep[e.g.][]{umstatter, walmswell, starfield, 2014arXiv1411.7447J}.

@@

\bibitem[\protect\citeauthoryear{Jones, Kashyap, 
\& van Dyk}{2014}]{2014arXiv1411.7447J} Jones D.~E., Kashyap V.~L., van Dyk D.~A., 2014, arXiv, arXiv:1411.7447
